---
title: "middle east analyses"
author: "Robert Mayer"
date: "12/11/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
options(scipen = 999)
library(dplyr)
library(ggplot2)
library(tidytext)
library(tidyr)
library(igraph)
library(ggraph)
library(wordcloud)
library(knitr)

knitr::opts_chunk$set(echo = FALSE)
load("data/corpus.rdata")

corpus %>% 
  filter(!grepl(c("date of foundation"),text)) %>% 
  filter(!grepl(c( "industry"),text)) %>% 
  filter(!grepl(c( "share holders"),text)) -> comments

corpus %>% 
  filter(grepl(("date of foundation+"),
               text)|grepl(( "industry+"),
                           text)|grepl(( "share holders+"),
                                       text)) -> information

```

## activity objectives

the report hereinafter shows result from the analyses performed with the aim of further investigage the drop in revenues during the first quarter of 2017

## analysed data


a sample of `r corpus$company %>% unique() %>% length()` companies was analysed, resorting to the customer cards produced from commercial department. In order to apply relevant text mining techniques described below a corpus of words was derived from those customer cards.

the corpus was composed of `r corpus %>% unnest_tokens(word, text, token = "words") %>% select(word) %>% nchar() %>% as.numeric() %>% round(2)` words.

## performed analyses

Starting from described dataset the following techniques was applied:

  - sentiment analysis, to discover the mood around the companies
  - wordcloud to understand how this mood was determined
  - ngram analysis needed to add context to most relevant words
  - network analyses on shareholders to observe structures within the relationship among companies and relevant shareholders

## results

reproduced below are results from mentioned analyses.

### sentiment analysis


```{r}
comments %>% 
  unnest_tokens(word,text)-> comments_tidy

#sentiment analysis  
  
lexicon <- get_sentiments("bing")

comments_tidy %>% 
  inner_join(lexicon) %>% 
  count(company,  sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive -negative)-> comments_sentiment

ggplot(comments_sentiment, aes(x = sentiment)) +
  geom_histogram()
```


### wordcloud


```{r}

comments_tidy %>%
  filter(!word %in% stop_words$word) %>%
  count(word) %>%
  with(wordcloud(word, n))
```

### ngram analysis

#### bigrams

```{r}
comments %>% 
unnest_tokens(bigram, text, token = "ngrams", n = 2) -> bigram_comments

bigram_comments %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  count(word1, word2, sort = TRUE) %>% 
  head() %>% 
  kable()
```

#### trigrams

```{r}

comments %>% 
  unnest_tokens(trigram, text, token = "ngrams", n = 3) -> trigram_comments

trigram_comments %>%
  separate(trigram, c("word1", "word2","word3"), sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  filter(!word3 %in% stop_words$word) %>% 
  count(word1, word2, word3, sort = TRUE) %>% 
  kable()
```

### network analysis


```{r}

information %>% 
  filter(grepl("share holders", text)) %>% 
  mutate(shareholders = gsub("share holders: ","",text)) %>% 
  separate(col = shareholders, into = c("first","second","third"),sep = ";") %>% 
  gather(key = "number",value ="shareholder",-company,-text) %>% 
  filter(!is.na(shareholder)) %>% 
  select(company,shareholder)-> shareholders

graph_from_data_frame(shareholders)-> graph_object

#linking the size of a node to its degree
 

 deg <- degree(graph_object, mode="all")
 V(graph_object)$size <- deg*3
 
 set.seed(30)
 graph_object %>% 
   ggraph() +
   geom_edge_link(alpha = .2) +
   geom_node_point(aes(size = size),alpha = .3) +
   geom_node_text(aes(label = name,size = size), vjust = 1, hjust = 1, check_overlap = FALSE)+
   theme_graph()

```



### data lineage

```{r}

information %>% 
  filter(grepl("industry", text)) %>% 
  mutate(industry = gsub("industry: ","",text))-> industries


industries %>% 
  inner_join(shareholders) %>% 
  select(-text)->data_lineage_data

inputPanel(
  selectInput("selected_industry", label = "select the industry you want to focus on", selected = "",
              choices = unique(data_lineage_data$industry)),
  
  textInput("name_string", label = "write the name of the shareholder",
              value = "")
)
renderDataTable(
 if (input$selected_industry != "" | input$name_string != ""){
 data_lineage_data %>% 
 filter(industry == input$selected_industry, grepl(input$name_string,shareholders))}else{(data_lineage_data)}
)
```




